---
title: "Analyses"
author: "Ian Hussey^[Ghent University. Email: ian.hussey@ugent.be]"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---

```{r, include=FALSE}
knitr::opts_chunk$set(message=FALSE,
                      warning=FALSE,
                      cache.lazy=FALSE)
```

```{r}

# dependencies
library(tidyverse)
library(knitr)
library(kableExtra)
library(timesavers)
library(psych)
library(lme4)
library(sjPlot)
library(sjstats)

# options
options(knitr.table.format = "html") # necessary configuration of tables

# disable scientific notation
options(scipen = 999) 

# get data
load("trimmed_data.RData") 

```

# Available N

```{r}

trimmed_data %>%
  summarize(n = n())

trimmed_data %>%
  group_by(domain) %>%
  summarize(n = n()) %>%
  summarize(max = max(n),
            min = min(n),
            mean = mean(n))

```

# Predicion 1b

"Scores on implicit measures assessing attitudes individuals regualrly think about are expected to have higher internal consistency ... than scores on implicit measures assessing attitudes individuals think only rarely about"

IC_low_frequency < IC_high_frequency

```{r}

# alpha values
D_alpha <- trimmed_data %>%
  select(domain, iat_type, D_first_half, D_second_half) %>%
  na.omit() %>%
  filter(iat_type == "Evaluation") %>%
  group_by(domain) %>%
  do(alpha = psych::alpha(., warnings = FALSE)$total$raw_alpha) %>%
  mutate(alpha = round(alpha, 3)) %>%
  ungroup() %>%
  rename(D_alpha = alpha)

# omega t data
est_omega_t <- function(data){
  require(timesavers)
  require(psych)
  results <- data %>%
    dplyr::select(-domain, -iat_type) %>%
    psych::omega(plot = FALSE)
  omega_t <- round(results$omega.tot, 3)
  return(omega_t)
}

D_omega_t <- trimmed_data %>%
  select(domain, iat_type, D_parcel_1, D_parcel_2, D_parcel_3) %>%
  na.omit() %>%
  filter(iat_type == "Evaluation") %>%
  group_by(domain, iat_type) %>%
  do(D_omega_t = est_omega_t(.)) %>%
  mutate(D_omega_t = round(D_omega_t, 3))

# frequency data
frequency_data <- trimmed_data %>%
  select(domain, iat_type, think_mean) %>%
  filter(iat_type == "Evaluation") %>%
  na.omit() %>%
  group_by(domain) %>%
  summarize(frequency_think = mean(think_mean)) %>%
  ungroup() %>%
  right_join(D_alpha, by = "domain") %>%
  right_join(D_omega_t, by = "domain")

```

## Alpha

```{r}

# model
fit_1 <- lm(frequency_think ~ D_alpha,
            data = frequency_data)

# table
tab_model(fit_1, 
          emph.p = FALSE, 
          show.std = TRUE,
          #show.se = TRUE,
          col.order = c("est", "se", "ci", "std.est", "std.se", "std.ci",
                        "stat", "p", "df", "response.level"))

# plot
plot_model(fit_1,
           type = "est")

```

## Omega t

```{r}

# model
fit_2 <- lm(frequency_think ~ D_omega_t,
            data = frequency_data)

# table
tab_model(fit_2, 
          emph.p = FALSE, 
          show.std = TRUE,
          #show.se = TRUE,
          col.order = c("est", "se", "ci", "std.est", "std.se", "std.ci",
                        "stat", "p", "df", "response.level"))

# plot
plot_model(fit_2,
           type = "est")

```

# Prediction 3

"Attitudes are expected to be less polarized than when individuals are given more time to answer the questions""

extremity_gut < extremity_actual

```{r}

# reshape data
domain_data <- trimmed_data %>%
  select(session_id, domain) %>%
  distinct()

extremity_ratings_data <- trimmed_data %>%
  select(session_id, domain, gut_x, gut_y, actual_x, actual_y) %>%
  na.omit() %>%
  # convert ratings of positive vs negative (1 to 10) to absolute extremity of ratings as they diverge from neturality:
  # split each scale at the mid point (5.5, given 1-10 response options) and find absolute values
  # then add 0.5 to give integer values.
  mutate(gut_x = abs(gut_x - 5.5) + 0.5,
         gut_y = abs(gut_y - 5.5) + 0.5,
         actual_x = abs(actual_x - 5.5) + 0.5,
         actual_y = abs(actual_y - 5.5) + 0.5) %>%
  group_by(session_id) %>%
  # average the extremity ratings for the two categories
  summarize(gut = mean(c(gut_x, gut_y)),
            actual = mean(c(actual_x, actual_y))) %>%
  ungroup() %>%
  gather(type, rating, c(actual, gut)) %>%
  # order the factors as gut > actual 
  mutate(type = fct_relevel(type,
                            "gut",
                            "actual"),
         type_numeric = ifelse(type == "gut", -0.5, 
                               ifelse(type == "actual", +0.5, NA))) %>%
  left_join(domain_data, by = "session_id")

# model
fit_3 <- lmer(rating ~ type + (type | domain),
              data = extremity_ratings_data)

# table
tab_model(fit_3, 
          emph.p = FALSE, 
          show.std = TRUE,
          #show.se = TRUE,
          col.order = c("est", "se", "ci", "std.est", "std.se", "std.ci",
                        "stat", "p", "df", "response.level"))

# plot
plot_model(fit_3,
           type = "est")

```


